\documentclass{resume}

% personal info header
\name{Bryce}{Hrusovsky}
\email{hrusovsk@msu.edu}
\social[linkedin][]{Bryce-Hrusovsky}


\begin{document}
\vspace*{-8mm}
\maketitle

\vspace*{-10mm}
\section{Education}

\cvitemwithcomment{}{\textbf{Michigan State University}}{\normalsize\textnormal{Aug 2013 - \textbf{Dec 2019}}}
\cvitem{}{\textit{Computer Science \& Engineering, B.S. | w/Business Cognate}}
\cvitem{}{\textit{GPA: 3.34/4.00 | Major GPA: 3.35/4.00}}

\vspace*{-4mm}
\section{Experience}

\cvitem{}{\textbf{Quavo}}
\cvitem{}{\textbf{Systems Architect Engineer, Intern}{\hspace*{90mm}}{\normalsize\textnormal{May 2019 - Present}}}
\begin{itemize}
    \item \cvitem{}{Built a \textbf{PEGA} application from the ground up laying the base foundation for the clients new back-end project.}
    \item \cvitem{}{Learned/Utilized PEGA development platform environment that's deployed using AWS. }
    \item \cvitem{}{Utilized client APIs for development of their new back-end.}
    \item \cvitem{}{Host online demonstrations of the product with clients between sprints, providing information for clients on the current status of the project.}
\end{itemize}

\vspace{2mm}

\cvitem{}{\textbf{Michigan State University}}
\cvitem{}{\textbf{Teaching Assistant - Trigonometry/Object Oriented Programming}{\hspace*{30mm}}{\normalsize\textnormal{Aug 2017 - May 2019}}}

\begin{itemize}
    \item \cvitem{}{Assist students in the design and implementation of their programming assignments using \textbf{C++}}
    \item \cvitem{}{Teach relevant CS patterns and fundamentals: abtract, composite, adaptor, etc...}
    \item \cvitem{}{Lecture, grade, and proctor for 60+ students on a weekly basis teaching/reviewing class information.}
\end{itemize}

\vspace*{4mm}
\cvitem{}{\textbf{Southern Glazers Wine \& Spirits}}
\cvitem{}{\textbf{Supply-Chain Management, Intern}{\hspace*{84mm}}{\normalsize\textnormal{June 2016 - Aug 2016}}}
\begin{itemize}
   \item \cvitem{}{Responsible for functional assignments within a 420,000 square ft wholesale distribution center at a 24/7 premier facility. Assisting with the processing of nearly 70k products daily.}
   \item \cvitem{}{Shadow line management gaining valuable leadership experience within the operations facility.}
   \item \cvitem{}{Prioritize projects to achieve goals within a deadline driven environment.}
\end{itemize}

\vspace*{-4mm}
\section{Projects}

\vspace{2mm}
\cvitemwithcomment{}{\textbf{SQLite Database}}{\normalsize\textnormal{Jan 2019 - May 2019}}
\begin{itemize}
    \item \cvitem{}{Created a SQLite-like database using \textbf{Python} that lexes, parses, and interprets SQL.}
    \item \cvitem{}{Implemented joins, transactions, concurrency control, custom aggregate functions, collations, views, etc.}
\end{itemize}

\vspace{2mm}
\cvitemwithcomment{}{\textbf{Michigan State Univesity Capstone Project}: Team Microsoft}{\normalsize\textnormal{Aug 2019 - Present}}
\cvitem{}{\textbf{ITPro Company Portal}}
\begin{itemize}
    \item \cvitem{}{Improve and build upon ITPro company portal UI on Android/IOS/Windows.}
    \item \cvitem{}{Completely renovate current project eliminating dead code, and increase overall efficiency.}
    \item \cvitem{}{Utilized technologies: Xamarin, C\#, Azure DevOps, Rest}
\end{itemize}


\vspace*{-4mm}
\section{Skills}
\begin{itemize}
    \item \cvitem{Languages}{Python, Pega, JavaScript, C/C++, Java, SQL, PHP}{}
    \item \cvitem{Other}{Git, Agile/Scrum, Linux/Unix, pytest, Amazon Web Services}{}
\end{itemize}

\vspace*{-4mm}
\section{Course Electives}
\vspace*{-3.5mm}
\begin{multicols}{2}
\begin{itemize}
    \item \cvitem{CSE 410}{Operating Systems}
    \item \cvitem{CSE 422}{Computer Networks}
    \item \cvitem{CSE 435}{Software Engineering}
    \item \cvitem{CSE 440}{Intro to AI}
    \item \cvitem{CSE 477}{Web App Architecture \& Develop}
    \item \cvitem{CSE 480}{Databases}
\end{itemize}
\end{multicols}
\end{document}
